\begin{abstractCZ}
    Tato práce se zabývá podrobnou analýzou současného informačního systému používaného
    na střední průmyslové škole. Hlavním cílem je poskytnout ucelený pohled na provoz
    systému, včetně popisu implementovaných funkcionalit, toku dat, synchronizačních 
    mechanismů, API funkcí, uživatelského rozhraní, legislativních požadavků a 
    bezpečnostních přístupů. V práci je kladen důraz na identifikaci silných a 
    slabých stránek současného systému a na porovnání s komerčními řešeními dostupnými
    na trhu. Dále se práce věnuje zhodnocení výhod a nevýhod vývoje vlastního informačního
    systému (in-house) ve srovnání s nákupem a implementací komerčního softwaru. Cílem 
    je poskytnout doporučení pro zlepšení stávajícího systému nebo pro výběr 
    vhodného komerčního řešení.
\end{abstractCZ}

\begin{keywordsCZ}
    informační systém, analýza, in-house vývoj, školství
\end{keywordsCZ}
    
    \vspace{2cm}
    
\begin{abstractEN}
    This thesis conducts a thorough analysis of the current information system
    used at a secondary technical school. The primary aim is to provide a comprehensive 
    overview of the system's operation, including a detailed description of the implemented 
    functionalities, data flow, synchronization mechanisms, API functions, user interface, 
    legislative requirements, and security approaches. The study focuses on identifying 
    the strengths and weaknesses of the current system and comparing it with commercial 
    solutions available in the market. Additionally, the thesis assesses the advantages 
    and disadvantages of developing an in-house information system versus purchasing and 
    implementing a commercial software solution. The goal is to provide recommendations 
    for improving the existing system or for selecting a suitable commercial solution.
\end{abstractEN}
    
\begin{keywordsEN}
    information system, analysis, in-house development, education
\end{keywordsEN}